---
title: "Examples"
author: "Toon Van Daele"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## List of formulas 


### Theis (1935)


$$
u^2 = \frac{S  r^2}{4  Kh  D  t}
$$

$$
s(r, t) = \frac{Q}{4 \pi Kh  D} * W(u)
$$



### Dupuit

$$
s(r) = D - \sqrt{D^2 - (\frac{Q}{\pi Kh}) log(\frac{r0}{r})}
$$


### Edelman


$$
s(r,t) = h_0 (1 - erf(r  \sqrt{\frac{S}{4 Kh D t}})
$$



### peilverlaging 

```{r}
r <- c(1, 10, 50, 100)
edelman_s(r = r, S = 0.25, Kh = 7, D = 50, t = 1, h0 = -1)
```



### Peilverhoging grafiek

```{r}
library(tidyverse)
library(hydranalytic)

t <- c(1, 4, 9, 16, 25, 36, 49, 64, 81, 100, 121)
r <- seq(from = 0, to = 700, by = 10)
Kh <- 7
D <- 100
S <- 0.25

df <- expand.grid(t = t, r = r, Kh = Kh, D = D, S = S)
df <- df %>%
  rowwise() %>%
  mutate(s = edelman_s(r = r, S = S, Kh = Kh, D = D, t = t, 1))

ggplot(data = df, aes(x = r, y = s, group = t, colour = t)) + geom_line() +
  scale_y_continuous(breaks=seq(from = 0, to = 1, by = 0.2)) +
  scale_x_continuous(breaks=seq(from = 0, to = 700, by = 100))

```



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
